Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2020-09-03 journal paper/content/sec-bg.tex
small comment on ts
Small edits.

We present self-contained background on multi-armed bandits (MAB), to make the paper accessible to researchers who are not experts on MAB.
We focus on the three classes of MAB algorithms listed in Section~\ref{sec:intro-model}: adaptive-exploration algorithms, exploration-separating algorithms, and greedy algorithms. We list the precise upper and lower bounds on the regret rates only to illustrate how the three algorithm classes are separated from one another; the exact results are not essential for the paper.

>>>>

We present self-contained background on multi-armed bandits (MAB), to make the paper accessible to researchers who are not experts on MAB.
We focus on the three classes of MAB algorithms listed in Section~\ref{expts-prelims}: adaptive-exploration algorithms, exploration-separating algorithms, and greedy algorithms. We list the precise upper and lower bounds on the regret rates only to illustrate how the three algorithm classes are separated from one another; the exact results are not essential for the paper.

### 2020-09-03 journal paper/content/sec-intro.tex
Small edits.

Each principal faces a basic and well-studied version of the multi-armed bandit problem, where each reward is drawn independently from a fixed, action-specific distribution. Each principal's strategy is a bandit algorithm; as such, it can dynamically adjust itself to the observed rewards, but not to the competition. This modeling choice reflects the reality of industrial applications, which build on a huge body of knowledge in machine learning. Responding to the competition is another layer of complexity which has not been previously studied in this context, let alone made practical. We draw on the machine learning literature to compare bandit algorithms to one another in the absence of competition, so that we can talk about \emph{better} bandit algorithms in a principled way.%
\footnote{Such comparisons are somewhat subtle, as some algorithms may be better for some problem instances and/or time intervals, and worse for some others. More on this in Preliminaries.}
%Generally,  ``better" algorithms are better in the long run, but could be worse initially. 
 One baseline is algorithms that do not explicitly explore (\emph{greedy algorithms}); in the absence of competition, they are known to be terrible for a wide variety of problem instances.}

@@

All results admit generalizations 
%extend to a much more general version of the multi-armed bandit problem 
in which the principal may observe additional feedback before and/or after each decision, as long as the feedback distribution does not change over time. In most results, principal's utility may depend on both the market share and agents' rewards.

>>>>

Each principal faces a basic and well-studied version of the multi-armed bandit problem, where each reward is drawn independently from a fixed, action-specific distribution. Each principal's strategy is a bandit algorithm; as such, it can dynamically adjust itself to the observed rewards, but not to the competition. This modeling choice reflects the reality of industrial applications, which build on a huge body of knowledge in machine learning. Responding to the competition is another layer of complexity which has not been previously studied in this context, let alone made practical. We draw on the machine learning literature to compare bandit algorithms to one another in the absence of competition, so that we can talk about \emph{better} bandit algorithms in a principled way. 
%\footnote{Such comparisons are somewhat subtle, as some algorithms may be better for some problem instances and/or time intervals, and worse for some others. More on this in Appendix~\ref{app:bg}. Generally,  ``better" algorithms are better in the long run, but could be worse initially. }
One baseline is algorithms that do not explicitly explore (\emph{greedy algorithms}); in the absence of competition, they are known to be terrible for a wide variety of problem instances.}

@@

Most results admit generalizations 
%extend to a much more general version of the multi-armed bandit problem 
in which the principal may observe additional feedback before and/or after each decision, 
%as long as the feedback distribution does not change over time. In most results,
 and principal's utility may include agents' rewards.
